---
# The title should have the first letter of each word capitalized, 
# except for conjunctions, prepositions, and articles
title: "Demo TRB Article to use as Template"
format:
  trb-pdf:
    keep-tex: true  
  trb-html: default
author:
  - name: John Doe
    corresponding: true
    affiliations:
      - name: State University
        department: Cool Dep
        address: Somewhere
        city: Magic city
        country: best one
        postal-code: 9999
    orcid: 0000-0000-0000-0000
    email: JD@example.org
    url: https://example.org/
    note: Assistant Professor
  - name: Emma Student
    affiliations:
      - State University
    email: 
    position: Student
abstract: |
  This document is only a demo explaining how to use the template.
keywords: [template, demo]
reference-section-title: References
date: 08/01/2023
wordcount: 5234
tablecount: 1
bibliography: bibliography.bib  
---

## Introduction {#sec-intro}

This is a template for a paper for the Annual Meeting of the Transportation
Research Board. The requirements for authors have become more flexible 
year by year, and the current requirements are only:

  - If you are using Large Language Models (LLMs) or Generative AI for your paper, refer to the guidelines below.
  - File Format: PDF
  - All papers must be submitted in English
  - Include a title page with title, authors, affiliations, and word count
  - Include all coauthor names, affiliations, and email addresses
  - ORCiD numbers are optional, but encouraged
  - Tables and figures should be embedded in the text, near the text that discusses the item
  - 8.5x11 page with normal margins
  - The title should have the first letter of each word capitalized, except for conjunctions, prepositions, and articles
  - Font: Times Roman font, 10 pt size or larger
  - Single spaced
  - Single column
  - Line numbers are required (restart numbering on each page)
  - Page numbers are required
  - Manuscript Length: The length of each paper, including the abstract, text, acknowledgments, references, and tables, must not exceed 7,500 words. Each table counts as 250 words. Papers not meeting this requirement may be withdrawn from the peer review process at any time. Abstract (250 words max). 
  - References should be numbered and called out in numerical order in the text
  - Supplemental Material/Appendices are not permitted in TRB Annual Meeting papers

This template generates a PDF matching all of these rules. The author must use the
`wordcount` and `tablecount` fields to specify the word count of their article,
but the total is calculated as per the formula defined above. 

## Demo of some features found in this demo journal template

The next several sections describe some features of the template. 

### Shortcode demo {#sec-shortcode}

PDF are rendered using {{< latex >}} but it is best if one can use a Markdown syntax for cross format support.

`{{< latex >}}` used in source is a shortcode syntax where the shortcode is included in the extension folder `_extensions`

### Code chunk {#sec-chunks}

This format hide chunks by default as option has been set in `_extension.yml` file.

```{r}
#| prompt: true
# Loading some data but this chunk won't be shown.
data("quine", package = "MASS")
```

But you can set `echo` option to `true` locally in the chunk

```{r}
#| echo: true
m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, family = poisson)
summary(m_pois)
```

I encourage you to use the `modelsummary` packages for generating model tables. 

### Text color {#sec-summary}

Our format makes applying color on inline text possible using the `[content]{color=<name>}` syntax. Let's see an example.

Here we are using a special feature of our format which is the coloring because [pink is a **nice** color]{color=mypink}.

This is possible thanks to the Lua Filter included in the custom extension format.

### Using references {.unnumbered}

I did not read this book [@CameronTrivedi2013] but it must be interesting. You can also refer to specific authors, as in @ben1997modeling, though many citation styles do not care one way or the other. We use Pandoc citeproc to
process the bibliography, and use the citation style language (csl) at [ http://www.zotero.org/styles/transportation-research-record](http://www.zotero.org/styles/transportation-research-record)